Lemma 1

### 2021-02-24 notes/jessie-russian-lemma.tex
Touching up proof

Fix $z$.
Consider the set-valued function $Q : \Omega \to 2^{\reals^d}$ defined by $Q(\omega) := \{v' \in \reals^d : \inprod{z}{v'} = L'(u,\omega,z) \}$.
Now, we want to take a measurable function $V$ that is a selection of $Q$ satisfying the following two conditions:
\begin{enumerate}
	\item $\E_p V \in \E_p \partial L(u,Y)$.
	\item $\inprod{z}{\E_p V} = \E_p L'(u,Y,z)$
\end{enumerate} 
If these are true, then we can take $v := \E_p V$ and observe the result.

Observe that $Q$ is solid-valued and therefore measurable iff $Q^{-1}(x) \in \B(\Omega)$ for all $x \in \reals^d$. \jessie{Rockafellar VA Example 14.7}.
\jessie{Assumptions that we're happy with} implies then that $Q$ is measurable; in turn, by \jessie{Rockafellar VA 14.6}, we have a measurable selection $V : \Omega \to \reals^d$ such that $\inprod{z}{V(\omega)} \in \partial L'(u,\omega, z)$ for all $\omega \in \Omega$.

First, we want to show $\E_p V \in \E_p \partial L(u,Y)$.
That is, $\int V(y) dpy \in \int \partial L(u,y) dpy = \{\E_p V(Y) : V \textrm{ measurable, }\, V(y) \in \partial L(u,y) p\textrm{-almost surely}\}$.
Since $V$ is measurable, it is just left to show $V(\omega) \in \partial L(u,\omega)$ $p$-almost surely.
By construction, for all $\omega \in \Omega$, we have $\inprod{V(\omega)}{z} = L'(u,\omega,z)$.
This implies 
\begin{align*}
\inprod{V(\omega)}{z} &= L'(u,\omega,z)\\
\inprod{V(\omega)}{z} &= \sup_{x \in \partial L(u,\omega)} \inprod{x}{z}\\
\implies \inprod{V(\omega)}{z} &\geq \inprod{x}{z} \; \forall x \in \partial L(u,\omega)\\
%\implies  \inprod{V(\omega)}{z} &\geq  \inprod{x}{z} \geq \jessie{??} \; \textrm{since } x \in \partial L(u,\omega)\\
\jessie{??}\\
\iff \inprod{V(\omega)}{(t-\omega)} &\leq L(u,t) - L(u,\omega)\,\forall t \in \reals^d\\
\iff V(\omega) &\in \{x \in \reals^d : \inprod{x}{(t - \omega)} \leq L(u,t) - L(u,\omega) \, \forall t \in \reals^d\}\\
V(\omega) &\in \partial L(u,\omega) \\ 
\end{align*}

\jessie{TODO}

Second, we want to show $\inprod{z}{v} = \E_p L'(u,Y,z)$.
\jessie{TODO}

>>>>

Fix $z$.
Consider the set-valued function $Q_z : \Omega \to 2^{\reals^d}$ defined by $Q_z(\omega) := \{v' \in \reals^d : \inprod{z}{v'} = L'(u,\omega;z) \}$.
Now, we want to take a measurable function $V$ that is a selection of $Q_z$ satisfying the following two conditions:
\begin{enumerate}
	\item $\E_p V \in \E_p \partial L(u,Y)$.
	\item $\inprod{z}{\E_p V} = \E_p L'(u,Y,z)$
\end{enumerate} 
If these are true, then we can take $v := \E_p V$ and observe the result.

Observe that $Q_z$ is solid-valued and therefore measurable iff $Q_z^{-1}(x) \in \B(\Omega)$ for all $x \in \reals^d$. \jessie{Rockafellar VA Example 14.7}.
\jessie{Assumptions that we're happy with} implies then that $Q_z$ is measurable; in turn, by \jessie{Rockafellar VA 14.6}, we have a measurable selection $V : \Omega \to \reals^d$ such that $\inprod{z}{V(\omega)} = L'(u,\omega; z)$ for all $\omega \in \Omega$.

First, we want to show $\E_p V \in \E_p \partial L(u,Y)$.
That is, $\int V(\omega) dp\omega \in \int \partial L(u,\omega) dp\omega = \{\E_p V(Y) : V \textrm{ measurable, }\, V(\omega) \in \partial L(u,\omega) \, p\textrm{-almost surely}\}$.
Since $V$ is measurable, it is just left to show $V(\omega) \in \partial L(u,\omega)$ $p$-almost surely.
By construction, for all $\omega \in \Omega$, we have $\inprod{V(\omega)}{z} = L'(u,\omega;z)$.
This implies 
\begin{align*}
\inprod{V(\omega)}{z} &= L'(u,\omega;z)\\
\inprod{V(\omega)}{z} &= \sup_{x \in \partial L(u,\omega)} \inprod{x}{z} \jessie{\textrm{Boyd and Vandenberghe slides}}\\
\implies \inprod{V(\omega)}{z} &\geq \inprod{x}{z} \; \forall x \in \partial L(u,\omega)\\
z := \omega - t \text{\footnotemark}\implies \inprod{V(\omega)}{\omega - t} &\geq \inprod{x}{\omega - t} \geq L(u,\omega) - L(u,t) \; \forall x \in \partial L(u,\omega)\\
\implies \inprod{V(\omega)}{\omega-t} &\geq L(u,\omega) - L(u,t)\,\forall t \in \reals^d\\
V(\omega) &\in \partial L(u,\omega) \\ 
\end{align*}
\footnotetext{can we do this?  since $z$ is fixed but $t$ is a variable}
\jessie{This is actually a bit stronger than we need; is that part of my issue?}

Second, we want to show $\inprod{z}{v} = \E_p L'(u,Y,z)$.
This follows from linearity of expectation and construction of $V$; to see this, consider
\begin{align*}
\inprod{z}{v} &= \inprod{z}{\E_p V} \\
 &= \E_p \inprod{z}{V} \\
 &= \int \inprod{z}{V(\omega)} dp\omega \\
 &= \int L'(u,\omega; z) dp\omega \\
 &= \E_p L'(u,Y;z)
\end{align*}
